%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, letterpaper]{awesome-cv}
\hypersetup
{
	pdfauthor={Matthew Kocubinski},
	pdftitle={Matthew Kocubinski - Software Engineer}
}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-red}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
\name{Matthew}{Kocubinski}
\position{Software Engineer{\enskip\cdotp\enskip}Systems Administrator}
\address{310 E 85th St, Apt. 4D, New York, NY 10028}

\mobile{(609) 802-4490} 
\email{matt.kocubinski@gmail.com}
\homepage{kocubinski.wordpress.com}
\github{kocubinski}
\linkedin{kocubinski}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \extrainfo{extra informations}

%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Matthew Kocubinski~~~·~~~Résumé}
  {\thepage}


%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Summary}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvparagraph}
\raggedright
Software engineer with 8 years of professional experience in full-stack development on both GNU/Linux
and Microsoft platforms.  Strong background in functional and object-oriented programming, long-term system architecture, data modeling.  Competent GNU/Linux systems administrator. 
%---------------------------------------------------------
\end{cvparagraph}


%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Skills}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvskills}

%---------------------------------------------------------
  \cvskill
    {Languages} % Category
    {C\#, F\#, C/C++, Java, Clojure, Clojurescript, Javascript, Python, SQL, Emacs Lisp, PHP, HTML/CSS, Perl, Ruby, AHDL, LaTeX} % Skills

%---------------------------------------------------------
  \cvskill
    {Platforms / Frameworks} % Category
    {.NET/CLR, JVM, GNU/Linux, ASP.NET, Node.js, Altera FPGAs, Django, ASP.NET, Windows Azure } % Skills

%---------------------------------------------------------
  \cvskill
    {Tools / Libraries} % Category
    {Emacs, Vim, ASP.NET, WPF, Windows Forms, MySQL, PostgreSQL, MS SQL, MongoDB, Apache, Nginx, Postfix, ElasticSearch, Windows Driver Kit (WDK), DirectX SDK, Torque Game Engine, TeamCity, git, SVN, Mercurial}

%---------------------------------------------------------
\end{cvskills}


%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
 \cventry
   {Developer}
   {Cordium}
   {New York, NY}
   {May 2016 - Current}
   {
     \begin {cvitems}
       \item {Ongoing development on a business-to-business product in the financial technology space.}
       \item {ASP.NET, MS SQL, WebForms}
     \end {cvitems}
   }
  \vspace{1mm}
  \cventry
    {Software Developer} % Job title
    {Dittman Incentive Marketing} % Organization
    {New Brunswick, NJ} % Location
    {Mar 2013 - May 2016} 
    {
      \begin{cvitems} 
        \item {Develop and maintain web applications for employee recognition in the business-to-business software space, built on Microsoft stack: C\#, ASP.NET, HTML/CSS, JavaScript, MS SQL}
        \item {Architect and build e-commerce platform used by many internal services.}
        \item {SQL Server administration}
        \item {Create and manage SDLC and deployment processes}
        \item {Direct major refactoring and future development to (re-)engineer code base into multi-tiered architecture using Dependency Injection, AOP, and OOP best practices.}
	\item {Introduce Test Driven Development, and test coverage for production sensitive areas of code base.}
      \end{cvitems}
    }
  \vspace{1mm}
%---------------------------------------------------------
  \cventry
    {Software Programmer} % Job title
    {PharmaSeq, Inc.} % Organization
    {Princeton, NJ} % Location
    {2010 - Mar 2013} % Date(s)
    {
      \begin{cvitems} 
        \item {Product development in biotechnology and RFID spaces.}
        \item {Work with micron-sized, laser light activated RFID chips with applications in object tagging / tracking, and fluorescence marked bioassays.}
        \item {Develop full-stack for two USB devices used to capture and stream data for real-time analysis.}
        \item {Develop control software for a Mitsubishi Industrial Pick and Place robot - Clojure, MELFA Basic}
        \item {USB Drivers - C/C++, WDK}
        \item {Desktop applications - .NET, C\#, F\#, Clojure, C++/CIL, Python, SQL, WPF, WinForms, DirectX}
        \item {Embedded software - AHDL, C}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Systems Administrator} % Job title
    {Packet Publications} % Organization
    {Princeton, NJ} % Location
    {2009 - 2010} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintain local area network infrastructure for 300+ clients}
        \item {Build and maintain servers for mail, data storage, publishing workflow, billing / account routines, backups.}
        \item {Work with Linux/Unix/Windows servers, and an open-source stack high-availability cluster.}
        \item {DNS, NFS, LDAP, Samba, AD}
        \item {Cisco IOS routing and firewalls}
        \item {Scripting in Perl, Bash, VBScript, Expect}
        \item {SQL, IBM Informix DBs}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}

\clearpage
%-------------------------------------------------------------------------------
%	PROJECTS
%-------------------------------------------------------------------------------
\cvsection{Projects}
\begin{cventries}
  \cventry
    {Author}
    {clojurewm}
    {\href{https://github.com/kocubinski/clojurewm}{github.com/kocubinski/clojurewm}}
    {}
    {
      \begin{cvitems}
        \item {A window manager for Microsoft Windows written in Clojure.}
        \item {Easily tag and recall many windows with keyboard shortcuts for a vastly improved, Alt-Tab free, computing experience.}
      \end{cvitems}
    }
  \vspace{1mm}
  \cventry
    {Developer}
    {Legions: Overdrive}
    {\href{http://www.legionsoverdrive.com}{www.legionsoverdrive.com}}
    {2011 - 2013}
    {
      \begin{cvitems}
        \item {Developer for the online multi-player first-person shooter game Legions: Overdrive.}
        \item {Modify and extend the Torque Game Engine (C/C++)}
        \item {Develop game launcher in C\#.NET to sync client with deployed version on SVN.  Maintain Django server to interface with launcher.}
        \item {Prototyping in the Unity 4 game engine}
      \end{cvitems}
    }
\end{cventries}


%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Associates of Music} % Degree
    {Mercer County Community College} % Institution
    {Hamilton, NJ} % Location
    {2003 - 2006} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {GPA 3.7}
        \item {Study of Jazz Performance on Drumset, Music Theory/History, Calculus 1-3}
      \end{cvitems}
    }
  \vspace{1mm}
  \cventry
    {Electrical Engineering} 
    {Rutgers University} % Institution
    {New Brunswick, NJ} % Location
    {2007 - 2008} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {GPA 3.8}
        \item {Fundamentals of Electrical Engineering, AC/DC, RLC Circuits, Filter Design, Digital Logic Design}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}





%-------------------------------------------------------------------------------
\end{document}
